The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-15 methods/ms.tex
changed PCA figures and added new map demo figure

Five image types will be released, each covering the same regions.  The maps
are standard astrophysical maps subject to the caveats previously mentioned,
the most important being the spatial filtering function (section \ref{sec:}).
The model maps are deconvolved using the maximum-entropy method with kernels
specified in the header.  The residual map is the map of the model timestream
subtracted from the data timestream; it is close to but not identical to the
map minus the model.  The weightmap shows the inverse-variance weighting of
each pixel.  The nhitsmap shows how many recorded data points from the
timestream have been assigned to each pixel; it is proportional to the dwell
time per pixel (each 'hit' is .1s).  Examples of each (except the nhitsmap)
are given in figure \ref{fig:sampleimages}.

>>>>

Five image types will be released, each covering the same regions.  The maps
are standard astrophysical maps subject to the caveats previously mentioned,
the most important being the spatial filtering function (section \ref{sec:Noise}).
The model maps are deconvolved using the maximum-entropy method with kernels
specified in the header.  The residual map is the map of the model timestream
subtracted from the data timestream; it is close to but not identical to the
map minus the model.  The weightmap shows the inverse-variance weighting of
each pixel.  The nhitsmap shows how many recorded data points from the
timestream have been assigned to each pixel; it is proportional to the dwell
time per pixel (each 'hit' is .1s).  Examples of each (except the nhitsmap)
are given in figure \ref{fig:sampleimages}.
